The kinematics of the Local Group in a cosmological context

### 2013-03-05 paper/ms.tex
minor updates

\begin{table}
\caption{Summary of results from the $\Lambda$CDM Bolshoi simulation}
\begin{center}
\begin{tabular}{cccc}\hline
 &  & Full Sample & Reduced Sample\\
$v_{\rm M31,rad}$ &(\kms) & $-70\pm 10$ & $-90\pm 10$\\
$v_{\rm M31,tan}$ &(\kms) & $50\pm 10$ & $50\pm 10$\\
$\log_{10}\lambda$& & $-1.47\pm 0.13$& $-1.34\pm 0.12$\\\hline
\end{tabular}
\end{center}
\vspace{1mm}
Note: the velocity uncertainties correspond to the minimal scale required to
obtain robust statistics in the upper panels of Figure \ref{fig:rt}
\label{table:2}
\end{table}

@@

From these results we infer that the pairs around the preferred phase
space for $\Lambda$CDM are at least $13$ times more common than pairs
with the observed velocities for the Local group. We highlight that
this is a lower bound given that in the reduced sample none of the
pairs is found in the interval allowed by observations. The high
eccentric orbit of the observed LG  constitutes an unlikely
configurations for the $\Lambda$CDM LG-like objects. This holds for
the full and the reduced sample of objects. {\bf This
  conclusions are valid at 1-$\sigma$ level in the observational
  uncertainties. Taking 3-$\sigma$ levels (i.e. uncertainties on the
  order of $\sigma_{\rm tan}=51$\kms and $\sigma_{\rm
    rad}=12$\kms the observational values are as likely as the
  preferred $\Lambda$CDM values, although only $\sim 6\%$ of the pairs
in the full and reduced samples would be consistent with observations.}

>>>>

\begin{table}
\caption{Summary of results from the $\Lambda$CDM Bolshoi simulation}
\begin{center}
\begin{tabular}{cccc}\hline
 &  & Full Sample & Reduced Sample\\
$v_{\rm M31,rad}$ &(\kms) & $-70\pm 10$ & $-90\pm 10$\\
$v_{\rm M31,tan}$ &(\kms) & $50\pm 10$ & $50\pm 10$\\
$\log_{10}\lambda$& & $-1.47\pm 0.13$& $-1.34\pm 0.12$\\\hline
\end{tabular}
\end{center}
\vspace{1mm}
Note: the velocity uncertainties correspond to the minimal bin size required to
obtain robust statistics in Figure \ref{fig:rt}
\label{table:2}
\end{table}

@@

From these results we infer that the pairs around the preferred phase
space for $\Lambda$CDM are at least $13$ times more common than pairs
with the observed velocities for the Local group. We highlight that
this is a lower bound given that in the reduced sample none of the
pairs is found in the interval allowed by observations. The high
eccentric orbit of the observed LG  constitutes an unlikely
configurations for the $\Lambda$CDM LG-like objects. This holds for
the full and the reduced sample of objects. {\bf These
  conclusions are valid at 1-$\sigma$ level in the observational
  uncertainties. An agreement between both samples of simulated LGs and the observed LG is reached only at the 3-sigma level.}
